---
title: "Exponential Random Graph Models (ERGM)"
author: "Blanca Arroyo-Correa"
date: "12/09/2023"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r initialize, message= FALSE, warning=FALSE}

library(plyr)
library(sand)
library(robustbase)
library(ergm) # Will load package 'network' as well.
library(ergm.count)
library(igraph)
library(ggplot2)
library(dplyr)
library(tidyr)
library(maditr)
library(textshape)
library(bipartite)
library(sjstats)
library(Hmisc)
library(network)
library(nlme)
library(ergm.count)
library(tibble)
library(tidyverse)
library(scales)
library(ggpubr)
library(ggthemes)
library(patchwork)
library(magrittr)
library(sf)
library(ggpubr)
library(ggthemes)
library(lmerTest)
library(lme4)
library(DHARMa)
range01 <- function(x){(x-min(x))/(max(x)-min(x))}

```

# Read interaction data

```{r read.int.data}

mat <- read.csv("Data/complete_interaction_matrix.csv", sep=",")
plant.info <- read.csv ("Data/individual_plants_id.csv", sep= ";")
plant.info <- plant.info %>% dplyr::select(Plant_sp, Plant_id, Plot)
glimpse(plant.info)

plant.traits <- read.csv("Data/plant_traits.csv", sep=",")
glimpse(plant.traits)

int.mat <- merge(mat, select(plant.info,Plant_sp, Plant_id), by="Plant_id") %>% filter(!Plant_sp %in% c("UPAR", "CSAL")) %>% droplevels() %>%
 select(where(~ any(. != 0))) %>% filter_all(any_vars(. != 0))
  
glimpse(int.mat)

```

# Set colour palettes

```{r colours}

cols <- data.frame(Plant_sp = sort(unique(unique(as.factor(plant.info$Plant_sp)))), 
                   stringsAsFactors = F)

cols2 <- cbind(cols, data.frame(color = c("cadetblue3", "dodgerblue3",
                                          "burlywood2", 
                                          "lightpink1", "brown2", 
                                          "darkolivegreen3", "forestgreen", 
                                          "orange", "darkorange2", "gray40", 
                                          "burlywood4")))
cols2 %<>% filter(Plant_sp != "CSAL", Plant_sp != "UPAR") %>% droplevels() %>% as.data.frame()

cols2 <- setNames((cols2$color), cols2$Plant_sp)

```

# Visitation matrix

```{r visit.mat}

# bipartite matrices per plot
bi.mat.plot <- list()
for (i in levels(as.factor(plant.info$Plot))){
  plot.id <- plant.info %>% filter(Plot== i) %>% filter(!Plant_id %in% c("UPAR", "CSAL"))
  temp <- int.mat %>% 
  filter(Plant_id %in% plot.id$Plant_id) %>% set_rownames(.$Plant_id) %>% 
  select(-Plant_sp, -Plant_id)
  bi.mat.plot[[i]] <- temp
}

# unipartite matrices per plot (lowest communality)
uni.mat.plot <- list()
for (i in seq_along(bi.mat.plot)){
  temp <- as.data.frame(as.one.mode(bi.mat.plot[[i]], fill = 0, project="lower", weighted=TRUE))
  uni.mat.plot[[i]] <- temp
}

```

# Co-flowering matrix

```{r flowering.mat}

flowers <- read.csv("Data/flowering_synchrony_plants.csv")[ ,1:6]

flowers %<>% mutate(Prop_flowers= N_flowers/Total_N_flowers) %>% filter(Plant_id %in% c(int.mat$Plant_id))

flowers %<>% mutate(Week=as.factor(Week))
str(flowers)

flowers2 <- flowers %>% select(Plant_id, Week, N_flowers) %>% 
  filter(N_flowers >0) %>% mutate(Week=as.numeric(Week))
glimpse(flowers2)
flowers2 %<>% group_by(Plant_id) %>% dplyr::summarise(start=min(Week), end=max(Week), duration=length(Week))

flowers.comb <- as.data.frame(t(combn(flowers2$Plant_id, 2))) 
flowers.comb %<>% dplyr::rename(Plant_id_1=V1, Plant_id_2=V2)

flowers.comb.sync <- flowers.comb %>% 
  left_join(flowers2, by=c("Plant_id_1"="Plant_id")) %>%
  dplyr::rename(start_1=start, end_1=end, duration_1=duration) %>% 
  left_join(flowers2, by=c("Plant_id_2"="Plant_id")) %>%
  dplyr::rename(start_2=start, end_2=end, duration_2=duration)


flowers.comb.sync %<>% rowwise() %>% dplyr::mutate(start_joint=max(start_1, start_2),
                              end_joint=min(end_1, end_2), duration_joint=max(duration_1, duration_2))
flowers.comb.sync %<>% rowwise() %>% mutate(overlap=end_joint-start_joint+1) 
flowers.comb.sync %<>% mutate(synchrony=overlap/duration_joint) %>% mutate(synchrony=ifelse(synchrony<0, 0, synchrony))


mygraph <- graph.data.frame(select(flowers.comb.sync, Plant_id_1, Plant_id_2, synchrony))
sync.index <- as.data.frame(get.adjacency(mygraph, sparse = FALSE, attr='synchrony'))
sync.index %<>% rownames_to_column("Plant_id")

# co-flowering matrix per plot

pheno.mat.plot <- list()
for (i in levels(as.factor(plant.info$Plot))){
  plot.id <- plant.info %>% filter(Plot== i)
  temp <- sync.index %>% 
  filter(Plant_id %in% plot.id$Plant_id) %>% set_rownames(.$Plant_id) %>% 
  select(any_of(plot.id$Plant_id))
  pheno.mat.plot[[i]] <- temp
}
```

# Spatial matrix

```{r spatial.mat}

plant.xy <- read.csv("Data/coordinates_plants.csv", sep=";") %>% filter(Plant_id %in% c(int.mat$Plant_id))

sf_data <- sf::st_as_sf(x = plant.xy, coords = c("X", "Y"),
                     crs = 3857)
dist.mat <- sf::st_distance(sf_data, sf_data, ) %>%
  as_tibble() %>% 
  purrr::set_names(nm = plant.xy$Plant_id) %>% 
  bind_cols(tibble(Plant_id = as.character(plant.xy$Plant_id)), . ) %>% as.data.frame()

# spatial matrix per plot
dist.mat.plot <- list()

for (i in levels(as.factor(plant.info$Plot))){
  plot.id <- plant.info %>% filter(Plot== i)
  temp <- dist.mat %>% 
  filter(Plant_id %in% plot.id$Plant_id) %>% set_rownames(.$Plant_id) %>% 
  select(any_of(plot.id$Plant_id))
  dist.mat.plot[[i]] <- temp
}

distances <- list()

for (i in seq_along(dist.mat.plot)){
  dist <- data.frame(plot=NA, max_dist=NA, min_dist=NA)
  dist$plot <- names(dist.mat.plot[i])
  dist$max_dist <- max(dist.mat.plot[[i]])
  temp <- c(as.matrix(dist.mat.plot[[i]]))
  dist$min_dist <- min(temp[temp >0])
  distances[[i]] <- dist
}

distances <- do.call("rbind", distances)
mean(distances$max_dist)
sd(distances$max_dist)
mean(distances$min_dist)
sd(distances$min_dist)


```

# Estimating average pollinator sharing

```{r average.pol.sharing}

freq.int <- int.mat %>% select(-Plant_sp) %>%
  dplyr::mutate(n_int = rowSums(across(where(is.numeric)), na.rm=TRUE)) %>% select(Plant_id, n_int) %>%
  mutate(n_int=round(n_int*1000,0))

# mean number of interactions shared (sum) and mean number of plants with shared interactions (count)
mean.A <- round(uni.mat.plot[[1]]*1000, 0) %>% mutate(count=rowSums(.!=0), sum=rowSums(.)) %>% select(count, sum) %>% summarise(mean_count=mean(count), mean_sum=mean(sum))
mean.B <- round(uni.mat.plot[[2]]*1000, 0) %>% mutate(count=rowSums(.!=0), sum=rowSums(.)) %>% select(count, sum) %>% summarise(mean_count=mean(count), mean_sum=mean(sum))
mean.C <- round(uni.mat.plot[[3]]*1000, 0) %>% mutate(count=rowSums(.!=0), sum=rowSums(.)) %>% select(count, sum) %>% summarise(mean_count=mean(count), mean_sum=mean(sum))
mean.D <- round(uni.mat.plot[[4]]*1000, 0) %>% mutate(count=rowSums(.!=0), sum=rowSums(.)) %>% select(count, sum) %>% summarise(mean_count=mean(count), mean_sum=mean(sum))
mean.E <- round(uni.mat.plot[[5]]*1000, 0) %>% mutate(count=rowSums(.!=0), sum=rowSums(.)) %>% select(count, sum) %>% summarise(mean_count=mean(count), mean_sum=mean(sum))
mean.F <- round(uni.mat.plot[[6]]*1000, 0) %>% mutate(count=rowSums(.!=0), sum=rowSums(.)) %>% select(count, sum) %>% summarise(mean_count=mean(count), mean_sum=mean(sum))

mean.all <- rbind(mean.A, mean.B, mean.C, mean.D, mean.E, mean.F) 
mean.all %>% dplyr::summarise(mean_all_count=mean(mean_count), sd_all_count=sd(mean_count),
                              mean_all_sum=mean(mean_sum), sd_all_sum=sd(mean_sum))

```

# Compute ERGMs

The unipartite projection of matrix A for the P plants contains the parallel minimum of the observed interactions between two individual plants, so that the level of pollinator sharing is driven by the lowest communality in interactions with pollinator species. In this unipartite network, two individual plants are linked if they share at least one interaction with the same pollinator species. 

We modelled the structure of the unipartite plant–plant network as a function of the sum of the link weights (weighted ERGMs) or the density of the network (binary ERGMs) as a structural covariate, the plant species identity and the number of flowers produced as node-based covariates, and the matrices of flowering overlap and spatial distance as dyadic covariates. We performed a binary ERGM and a weighted ERGM for each study plot.

# PLOT A
## Unipartite network: generate the unipartite projection of the plant-pollinator interaction matrix

```{r uni.graph.A, echo=TRUE, message= FALSE, warning= TRUE}

uni <- round((uni.mat.plot[[1]]) *1000, 0)
uni %<>% select(order(colnames(uni))) %>% as.matrix()

attr <- uni.mat.plot[[1]] %>% rownames_to_column("Plant_id") %>% left_join(filter(plant.info, Plot=="A")) %>%
  left_join(select(plant.traits, Plant_id, N_flowers))
attr %>% group_by(Plant_sp) %>%
  mutate(N_flowers = range01(N_flowers))

# remove column and row names
colnames(uni)<-NULL
rownames(uni)<-NULL

```

## Unipartite network: set node attributes in igraph object

```{r uni.nodes.A, echo=TRUE, message= FALSE, warning= TRUE}

uni.g <- graph.adjacency(uni, mode = "undirected", weighted = TRUE, diag = FALSE) # igraph object

V(uni.g)$Plant_id <- attr$Plant_id
V(uni.g)$Plant_sp <- attr$Plant_sp
V(uni.g)$N_flowers <- attr$N_flowers

```

## Unipartite network: set matrices and graphs for model testing (create network object) 

```{r uni.net.A, echo=TRUE, message= FALSE, warning= TRUE}


uni.AA <- get.adjacency(uni.g, attr = "weight") # First separate the igraph object into adjacency matrix and plant attributes

uni.v.attrs <- get.data.frame(uni.g, what="vertices")

uni.net <- network::as.network(as.matrix(uni.AA),
                             directed=FALSE, ignore.eval=FALSE, names.eval='weight')   # network object for ergm 

as.matrix(uni.net,attrname="weight") # We can view the weight attribute as a matrix


network::set.vertex.attribute(uni.net, "Plant_id",
                                uni.v.attrs$Plant_id)
network::set.vertex.attribute(uni.net, "Plant_sp",
                                uni.v.attrs$Plant_sp)
network::set.vertex.attribute(uni.net, "N_flowers",
                                uni.v.attrs$N_flowers)

# To include the effects of the spatial and flowering overlap between plant individuals on pollinator sharing

dist <- dist.mat.plot[[1]] 
dist %<>% select(order(colnames(dist)))
dist <- dist[order(rownames(dist)),]

pheno <- pheno.mat.plot[[1]]
pheno %<>% select(order(colnames(pheno)))
pheno <- pheno[order(rownames(pheno)),]

network::set.network.attribute(uni.net, "distance", as.matrix(dist)) # spatial distance between plants as network attribute
network::get.network.attribute(uni.net, "distance")

network::set.network.attribute(uni.net, "pheno", as.matrix(pheno)) # flowering overlap between plants as network attribute
network::get.network.attribute(uni.net, "pheno")

# evaluation of predictor matrices within and between plant species

sp <- uni.net %v% "Plant_sp"
uni.net %n% "spatial_distance_within" <- range01(uni.net %n% "distance" * outer(sp, sp, `==`))
uni.net %n% "spatial_distance_between" <- range01(uni.net %n% "distance" * outer(sp, sp, `!=`))

uni.net %n% "fl_overlap_within" <- range01(uni.net %n% "pheno" * outer(sp, sp, `==`))
uni.net %n% "fl_overlap_between" <- range01(uni.net %n% "pheno" * outer(sp, sp, `!=`))



```

## Unipartite network: predictor variables for valued ERGMs

```{r uni.models.A, echo=TRUE, message= FALSE, warning= TRUE}


uni.ergm0 <- formula(uni.net ~ sum) 


# test main effects of plant traits in sharing pollinators
# weighted
uni.ergmA <- formula(uni.net ~ sum 
                     + nodematch("Plant_sp", form= "sum")
                     + nodecov("N_flowers", form= "sum")
                     + edgecov("spatial_distance_within", form="sum")
                     + edgecov("spatial_distance_between", form="sum")
                     + edgecov("fl_overlap_within", form="sum")
                     + edgecov("fl_overlap_between", form="sum"))
# binary
uni.ergmA.b <- formula(uni.net ~ edges
                     + nodematch("Plant_sp")
                     + nodecov("N_flowers")
                     + edgecov("spatial_distance_within")
                     + edgecov("spatial_distance_between")
                     + edgecov("fl_overlap_within")
                     + edgecov("fl_overlap_between"))


```

## Unipartite network: compute ERGMs

```{r uni.model.tests.A, echo=TRUE, message= FALSE, warning= TRUE}

set.seed(42)
uni.ergm.fitA <- ergm::ergm(uni.ergmA, response ="weight", reference= ~Poisson)   
uni.ergm.fitA.b <- ergm(uni.ergmA.b)   

summary(uni.ergm.fitA) 
summary(uni.ergm.fitA.b) 

mcmc.diagnostics(uni.ergm.fitA)

## predict weighted model

sim.A <- simulate(uni.ergm.fitA, nsim=100, response = "weight", output="edgelist")

sim.A.mat <- list()
for (i in seq_along(sim.A)){
  temp <- get.adjacency(graph.data.frame(sim.A[[i]]), sparse = FALSE, attr='weight')
  sim.A.mat[[i]] <- temp
}
sim.A.mat.mean <- apply(simplify2array(sim.A.mat), 1:2, mean)

sim.A.mat.mean %<>% as.data.frame() %>% rename_at(vars(names(.)), ~attr$Plant_id) %>%
  magrittr::set_rownames(attr$Plant_id) 

sim.A.mat.mean <- get.data.frame(graph.adjacency(as.matrix(sim.A.mat.mean),weighted=TRUE)) %>% 
  rename(Plant_id_1=from, Plant_id_2=to, prob=weight) 

sim.A.mat.mean %<>% left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_1"= "Plant_id")) %>%
  rename(Plant_sp_1 = Plant_sp) %>% 
  left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_2"= "Plant_id")) %>%
  rename(Plant_sp_2 = Plant_sp) %>% mutate(het_con = ifelse(Plant_sp_1==Plant_sp_2, "con", "het")) %>%
  filter(Plant_id_1 != Plant_id_2)

sim.A.summ <- sim.A.mat.mean %>% group_by(Plant_id_1, het_con) %>%
  summarise(mean = mean(prob, na.rm=T)) %>% left_join(freq.int, by=c("Plant_id_1"="Plant_id"))

## predict binary model

predict.A <- predict(uni.ergm.fitA.b, conditional = TRUE, output = "matrix")
predict.A %<>% as.data.frame() %>% rename_at(vars(names(.)), ~attr$Plant_id) %>%
  magrittr::set_rownames(attr$Plant_id) %>% mutate(Plant_id_1=attr$Plant_id) %>% 
  pivot_longer(!Plant_id_1, names_to = "Plant_id_2", values_to = "prob")

predict.A %<>% left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_1"= "Plant_id")) %>%
  rename(Plant_sp_1 = Plant_sp) %>% 
  left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_2"= "Plant_id")) %>%
  rename(Plant_sp_2 = Plant_sp) %>% mutate(het_con = ifelse(Plant_sp_1==Plant_sp_2, "con", "het")) %>%
  filter(Plant_id_1 != Plant_id_2)

predict.A.summ <- predict.A %>% group_by(Plant_id_1, het_con) %>%
  summarise(mean = mean(prob, na.rm=T)) %>% left_join(freq.int, by=c("Plant_id_1"="Plant_id"))

```

# PLOT B
## Unipartite network: generate the unipartite projection of the plant-pollinator interaction matrix

```{r uni.graph.B, echo=TRUE, message= FALSE, warning= TRUE}

uni <- round((uni.mat.plot[[2]]) *1000, 0)
uni %<>% select(order(colnames(uni))) %>% as.matrix()

attr <- uni.mat.plot[[2]] %>% rownames_to_column("Plant_id") %>% left_join(filter(plant.info, Plot=="B")) %>%
  left_join(select(plant.traits, Plant_id, N_flowers))
attr %<>% group_by(Plant_sp) %>%
  mutate(N_flowers = range01(N_flowers))
# only conspecific individuals

#attr <- filter(attr, Plant_sp=="HPIC")
#uni %<>% 
#    filter(rownames(uni) %in% attr$Plant_id) %>% 
#    select(any_of(attr$Plant_id)) %>% as.matrix()

# remove column and row names
colnames(uni)<-NULL
rownames(uni)<-NULL

```

## Unipartite network: set node attributes in igraph object

```{r uni.nodes.B, echo=TRUE, message= FALSE, warning= TRUE}

uni.g <- graph.adjacency(uni, mode = "undirected", weighted = TRUE, diag = FALSE) # igraph object

V(uni.g)$Plant_id <- attr$Plant_id
V(uni.g)$Plant_sp <- attr$Plant_sp
V(uni.g)$N_flowers <- attr$N_flowers

```

## Unipartite network: set matrices and graphs for model testing (create network object) 

```{r uni.net.B, echo=TRUE, message= FALSE, warning= TRUE}


uni.AA <- get.adjacency(uni.g, attr = "weight") # First separate the igraph object into adjacency matrix and plant attributes

uni.v.attrs <- get.data.frame(uni.g, what="vertices")


uni.net <- network::as.network(as.matrix(uni.AA),
                             directed=FALSE, ignore.eval=FALSE, names.eval='weight')   # network object for ergm 


as.matrix(uni.net,attrname="weight") # We can view the weight attribute as a matrix
#get.edge.attribute(uni.s, "weight")


network::set.vertex.attribute(uni.net, "Plant_id",
                                uni.v.attrs$Plant_id)
network::set.vertex.attribute(uni.net, "Plant_sp",
                                uni.v.attrs$Plant_sp)
network::set.vertex.attribute(uni.net, "N_flowers",
                                uni.v.attrs$N_flowers)

# To include the effects of the spatial and flowering overlap between plant individuals on pollinator sharing

dist <- dist.mat.plot[[2]] 
dist %<>% select(order(colnames(dist)))
dist <- dist[order(rownames(dist)),]

pheno <- pheno.mat.plot[[2]]
pheno %<>% select(order(colnames(pheno)))
pheno <- pheno[order(rownames(pheno)),]

network::set.network.attribute(uni.net, "distance", as.matrix(dist)) # spatial distance between plants as network attribute
network::get.network.attribute(uni.net, "distance")

network::set.network.attribute(uni.net, "pheno", as.matrix(pheno)) # flowering overlap between plants as network attribute
network::get.network.attribute(uni.net, "pheno")

# evaluation of predictor matrices within and between plant species

sp <- uni.net %v% "Plant_sp"
uni.net %n% "spatial_distance_within" <- range01(uni.net %n% "distance" * outer(sp, sp, `==`))
uni.net %n% "spatial_distance_between" <- range01(uni.net %n% "distance" * outer(sp, sp, `!=`))

uni.net %n% "fl_overlap_within" <- range01(uni.net %n% "pheno" * outer(sp, sp, `==`))
uni.net %n% "fl_overlap_between" <- range01(uni.net %n% "pheno" * outer(sp, sp, `!=`))



```

## Unipartite network: predictor variables for valued ERGMs

```{r uni.models.B, echo=TRUE, message= FALSE, warning= TRUE}


uni.ergm0 <- formula(uni.net ~ sum) 


# test main effects of plant traits in sharing pollinators
uni.ergmB <- formula(uni.net ~ sum 
                     + nodematch("Plant_sp", form= "sum")
                     + nodecov("N_flowers", form= "sum")
                     + edgecov("spatial_distance_within", form="sum")
                     + edgecov("spatial_distance_between", form="sum")
                     + edgecov("fl_overlap_within", form="sum")
                     + edgecov("fl_overlap_between", form="sum"))

uni.ergmB.b <- formula(uni.net ~ edges
                     + nodematch("Plant_sp")
                     + nodecov("N_flowers")
                     + edgecov("spatial_distance_within")
                     + edgecov("spatial_distance_between")
                     + edgecov("fl_overlap_within")
                     + edgecov("fl_overlap_between"))

```

## Unipartite network: compute ERGMs

```{r uni.model.tests.B, echo=TRUE, message= FALSE, warning= TRUE}

set.seed(42)
uni.ergm.fitB <- ergm(uni.ergmB, response ="weight", reference= ~Poisson)   # quantitative
uni.ergm.fitB.b <- ergm(uni.ergmB.b)   # binary

summary(uni.ergm.fitB) 
summary(uni.ergm.fitB.b) 

mcmc.diagnostics(uni.ergm.fitB)

## predict weighted model

sim.B <- simulate(uni.ergm.fitB, nsim=100, response = "weight", output="edgelist")

sim.B.mat <- list()
for (i in seq_along(sim.B)){
  temp <- get.adjacency(graph.data.frame(sim.B[[i]]), sparse = FALSE, attr='weight')
  sim.B.mat[[i]] <- temp
}
sim.B.mat.mean <- apply(simplify2array(sim.B.mat), 1:2, mean)

sim.B.mat.mean %<>% as.data.frame() %>% rename_at(vars(names(.)), ~attr$Plant_id) %>%
  magrittr::set_rownames(attr$Plant_id) 

sim.B.mat.mean <- get.data.frame(graph.adjacency(as.matrix(sim.B.mat.mean),weighted=TRUE)) %>% 
  rename(Plant_id_1=from, Plant_id_2=to, prob=weight) 
#%>% mutate(prob=range01(prob))

sim.B.mat.mean %<>% left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_1"= "Plant_id")) %>%
  rename(Plant_sp_1 = Plant_sp) %>% 
  left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_2"= "Plant_id")) %>%
  rename(Plant_sp_2 = Plant_sp) %>% mutate(het_con = ifelse(Plant_sp_1==Plant_sp_2, "con", "het")) %>%
  filter(Plant_id_1 != Plant_id_2)

sim.B.summ <- sim.B.mat.mean %>% group_by(Plant_id_1, het_con) %>%
  summarise(mean = mean(prob, na.rm=T)) %>% left_join(freq.int, by=c("Plant_id_1"="Plant_id"))


## predict binary model

predict.B <- predict(uni.ergm.fitB.b, conditional = TRUE, output = "matrix")

predict.B %<>% as.data.frame() %>% rename_at(vars(names(.)), ~attr$Plant_id) %>%
  magrittr::set_rownames(attr$Plant_id) %>% mutate(Plant_id_1=attr$Plant_id) %>% 
  pivot_longer(!Plant_id_1, names_to = "Plant_id_2", values_to = "prob")

predict.B %<>% left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_1"= "Plant_id")) %>%
  rename(Plant_sp_1 = Plant_sp) %>% 
  left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_2"= "Plant_id")) %>%
  rename(Plant_sp_2 = Plant_sp) %>% mutate(het_con = ifelse(Plant_sp_1==Plant_sp_2, "con", "het")) %>%
  filter(Plant_id_1 != Plant_id_2)

predict.B.summ <- predict.B %>% group_by(Plant_id_1, het_con) %>%
  summarise(mean = mean(prob, na.rm=T)) %>% left_join(freq.int, by=c("Plant_id_1"="Plant_id"))


```

# PLOT C
## Unipartite network: generate the unipartite projection of the plant-pollinator interaction matrix

```{r uni.graph.C, echo=TRUE, message= FALSE, warning= TRUE}

uni <- round((uni.mat.plot[[3]]) *1000, 0)
uni %<>% select(order(colnames(uni))) %>% as.matrix()

attr <- uni.mat.plot[[3]] %>% rownames_to_column("Plant_id") %>% left_join(filter(plant.info, Plot=="C")) %>%
  left_join(select(plant.traits, Plant_id, N_flowers))
attr %<>% group_by(Plant_sp) %>%
  mutate(N_flowers = range01(N_flowers))
# only conspecific individuals

#attr <- filter(attr, Plant_sp=="HPIC")
#uni %<>% 
#    filter(rownames(uni) %in% attr$Plant_id) %>% 
#    select(any_of(attr$Plant_id)) %>% as.matrix()

# remove column and row names
colnames(uni)<-NULL
rownames(uni)<-NULL

```

## Unipartite network: set node attributes in igraph object

```{r uni.nodes.C, echo=TRUE, message= FALSE, warning= TRUE}

uni.g <- graph.adjacency(uni, mode = "undirected", weighted = TRUE, diag = FALSE) # igraph object

V(uni.g)$Plant_id <- attr$Plant_id
V(uni.g)$Plant_sp <- attr$Plant_sp
V(uni.g)$N_flowers <- attr$N_flowers

```

## Unipartite network: set matrices and graphs for model testing (create network object) 

```{r uni.net.C, echo=TRUE, message= FALSE, warning= TRUE}


uni.AA <- get.adjacency(uni.g, attr = "weight") # First separate the igraph object into adjacency matrix and plant attributes

uni.v.attrs <- get.data.frame(uni.g, what="vertices")


uni.net <- network::as.network(as.matrix(uni.AA),
                             directed=FALSE, ignore.eval=FALSE, names.eval='weight')   # network object for ergm 


as.matrix(uni.net,attrname="weight") # We can view the weight attribute as a matrix
#get.edge.attribute(uni.s, "weight")


network::set.vertex.attribute(uni.net, "Plant_id",
                                uni.v.attrs$Plant_id)
network::set.vertex.attribute(uni.net, "Plant_sp",
                                uni.v.attrs$Plant_sp)
network::set.vertex.attribute(uni.net, "N_flowers",
                                uni.v.attrs$N_flowers)

# To include the effects of the spatial and flowering overlap between plant individuals on pollinator sharing

dist <- dist.mat.plot[[3]] 
dist %<>% select(order(colnames(dist)))
dist <- dist[order(rownames(dist)),]

pheno <- pheno.mat.plot[[3]]
pheno %<>% select(order(colnames(pheno)))
pheno <- pheno[order(rownames(pheno)),]

network::set.network.attribute(uni.net, "distance", as.matrix(dist)) # spatial distance between plants as network attribute
network::get.network.attribute(uni.net, "distance")

network::set.network.attribute(uni.net, "pheno", as.matrix(pheno)) # flowering overlap between plants as network attribute
network::get.network.attribute(uni.net, "pheno")

# evaluation of predictor matrices within and between plant species

sp <- uni.net %v% "Plant_sp"
uni.net %n% "spatial_distance_within" <- range01(uni.net %n% "distance" * outer(sp, sp, `==`))
uni.net %n% "spatial_distance_between" <- range01(uni.net %n% "distance" * outer(sp, sp, `!=`))

uni.net %n% "fl_overlap_within" <- range01(uni.net %n% "pheno" * outer(sp, sp, `==`))
uni.net %n% "fl_overlap_between" <- range01(uni.net %n% "pheno" * outer(sp, sp, `!=`))


```

## Unipartite network: predictor variables for valued ERGMs

```{r uni.models.C, echo=TRUE, message= FALSE, warning= TRUE}


uni.ergm0 <- formula(uni.net ~ sum) 


# test main effects of plant traits in sharing pollinators
uni.ergmC <- formula(uni.net ~ sum 
                     + nodematch("Plant_sp", form= "sum")
                     + nodecov("N_flowers", form= "sum")
                     + edgecov("spatial_distance_within", form="sum")
                     + edgecov("spatial_distance_between", form="sum")
                     + edgecov("fl_overlap_within", form="sum")
                     + edgecov("fl_overlap_between", form="sum"))

uni.ergmC.b <- formula(uni.net ~ edges
                     + nodematch("Plant_sp")
                     + nodecov("N_flowers")
                     + edgecov("spatial_distance_within")
                     + edgecov("spatial_distance_between")
                     + edgecov("fl_overlap_within")
                     + edgecov("fl_overlap_between"))

```

## Unipartite network: compute ERGMs

```{r uni.model.tests.C, echo=TRUE, message= FALSE, warning= TRUE}

set.seed(42)
uni.ergm.fitC <- ergm(uni.ergmC, response ="weight", reference= ~Poisson)   
uni.ergm.fitC.b <- ergm(uni.ergmC.b)   

summary(uni.ergm.fitC) 
summary(uni.ergm.fitC.b) 

mcmc.diagnostics(uni.ergm.fitC)

## predict weighted model

sim.C <- simulate(uni.ergm.fitC, nsim=100, response = "weight", output="edgelist")

sim.C.mat <- list()
for (i in seq_along(sim.C)){
  temp <- get.adjacency(graph.data.frame(sim.C[[i]]), sparse = FALSE, attr='weight')
  sim.C.mat[[i]] <- temp
}
sim.C.mat.mean <- apply(simplify2array(sim.C.mat), 1:2, mean)

sim.C.mat.mean %<>% as.data.frame() %>% rename_at(vars(names(.)), ~attr$Plant_id) %>%
  magrittr::set_rownames(attr$Plant_id) 

sim.C.mat.mean <- get.data.frame(graph.adjacency(as.matrix(sim.C.mat.mean),weighted=TRUE)) %>% 
  rename(Plant_id_1=from, Plant_id_2=to, prob=weight) 
#%>% mutate(prob=range01(prob))

sim.C.mat.mean %<>% left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_1"= "Plant_id")) %>%
  rename(Plant_sp_1 = Plant_sp) %>% 
  left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_2"= "Plant_id")) %>%
  rename(Plant_sp_2 = Plant_sp) %>% mutate(het_con = ifelse(Plant_sp_1==Plant_sp_2, "con", "het")) %>%
  filter(Plant_id_1 != Plant_id_2)

sim.C.summ <- sim.C.mat.mean %>% group_by(Plant_id_1, het_con) %>%
  summarise(mean = mean(prob, na.rm=T)) %>% left_join(freq.int, by=c("Plant_id_1"="Plant_id"))

## predict binary model

predict.C <- predict(uni.ergm.fitC.b, conditional = TRUE, output = "matrix")

predict.C %<>% as.data.frame() %>% rename_at(vars(names(.)), ~attr$Plant_id) %>%
  magrittr::set_rownames(attr$Plant_id) %>% mutate(Plant_id_1=attr$Plant_id) %>% 
  pivot_longer(!Plant_id_1, names_to = "Plant_id_2", values_to = "prob")

predict.C %<>% left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_1"= "Plant_id")) %>%
  rename(Plant_sp_1 = Plant_sp) %>% 
  left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_2"= "Plant_id")) %>%
  rename(Plant_sp_2 = Plant_sp) %>% mutate(het_con = ifelse(Plant_sp_1==Plant_sp_2, "con", "het")) %>%
  filter(Plant_id_1 != Plant_id_2)

predict.C.summ <- predict.C %>% group_by(Plant_id_1, het_con) %>%
  summarise(mean = mean(prob, na.rm=T)) %>% left_join(freq.int, by=c("Plant_id_1"="Plant_id"))

```

# PLOT D
## Unipartite network: generate the unipartite projection of the plant-pollinator interaction matrix

```{r uni.graph.D, echo=TRUE, message= FALSE, warning= TRUE}

uni <- round((uni.mat.plot[[4]]) *1000, 0)
uni %<>% select(order(colnames(uni))) %>% as.matrix()

attr <- uni.mat.plot[[4]] %>% rownames_to_column("Plant_id") %>% left_join(filter(plant.info, Plot=="D")) %>%
  left_join(select(plant.traits, Plant_id, N_flowers))
attr %<>% group_by(Plant_sp) %>%
  mutate(N_flowers = range01(N_flowers))

# only conspecific individuals

#attr <- filter(attr, Plant_sp=="HPIC")
#uni %<>% 
#    filter(rownames(uni) %in% attr$Plant_id) %>% 
#    select(any_of(attr$Plant_id)) %>% as.matrix()

# remove column and row names
colnames(uni)<-NULL
rownames(uni)<-NULL

```

## Unipartite network: set node attributes in igraph object

```{r uni.nodes.D, echo=TRUE, message= FALSE, warning= TRUE}

uni.g <- graph.adjacency(uni, mode = "undirected", weighted = TRUE, diag = FALSE) # igraph object

V(uni.g)$Plant_id <- attr$Plant_id
V(uni.g)$Plant_sp <- attr$Plant_sp
V(uni.g)$N_flowers <- attr$N_flowers

```

## Unipartite network: set matrices and graphs for model testing (create network object) 

```{r uni.net.D, echo=TRUE, message= FALSE, warning= TRUE}

uni.AA <- get.adjacency(uni.g, attr = "weight") # First separate the igraph object into adjacency matrix and plant attributes

uni.v.attrs <- get.data.frame(uni.g, what="vertices")


uni.net <- network::as.network(as.matrix(uni.AA),
                             directed=FALSE, ignore.eval=FALSE, names.eval='weight')   # network object for ergm 


as.matrix(uni.net,attrname="weight") # We can view the weight attribute as a matrix
#get.edge.attribute(uni.s, "weight")


network::set.vertex.attribute(uni.net, "Plant_id",
                                uni.v.attrs$Plant_id)
network::set.vertex.attribute(uni.net, "Plant_sp",
                                uni.v.attrs$Plant_sp)
network::set.vertex.attribute(uni.net, "N_flowers",
                                uni.v.attrs$N_flowers)

# To include the effects of the spatial and flowering overlap between plant individuals on pollinator sharing

dist <- dist.mat.plot[[4]] 
dist %<>% select(order(colnames(dist)))
dist <- dist[order(rownames(dist)),]

pheno <- pheno.mat.plot[[4]]
pheno %<>% select(order(colnames(pheno)))
pheno <- pheno[order(rownames(pheno)),]

vegan::mantel(as.matrix(pheno), as.matrix(dist))

network::set.network.attribute(uni.net, "distance", as.matrix(dist)) # spatial distance between plants as network attribute
network::get.network.attribute(uni.net, "distance")

network::set.network.attribute(uni.net, "pheno", as.matrix(pheno)) # flowering overlap between plants as network attribute
network::get.network.attribute(uni.net, "pheno")

# evaluation of predictor matrices within and between plant species

sp <- uni.net %v% "Plant_sp"
uni.net %n% "spatial_distance_within" <- range01(uni.net %n% "distance" * outer(sp, sp, `==`))
uni.net %n% "spatial_distance_between" <- range01(uni.net %n% "distance" * outer(sp, sp, `!=`))

uni.net %n% "fl_overlap_within" <- range01(uni.net %n% "pheno" * outer(sp, sp, `==`))
uni.net %n% "fl_overlap_between" <- range01(uni.net %n% "pheno" * outer(sp, sp, `!=`))


```

## Unipartite network: predictor variables for valued ERGMs

```{r uni.models.D, echo=TRUE, message= FALSE, warning= TRUE}


uni.ergm0 <- formula(uni.net ~ sum) 


# test main effects of plant traits in sharing pollinators
uni.ergmD <- formula(uni.net ~ sum 
                     + nodematch("Plant_sp", form= "sum")
                     + nodecov("N_flowers", form= "sum")
                     + edgecov("spatial_distance_within", form="sum")
                     + edgecov("spatial_distance_between", form="sum")
                     + edgecov("fl_overlap_within", form="sum")
                     + edgecov("fl_overlap_between", form="sum"))

uni.ergmD.b <- formula(uni.net ~ edges
                     + nodematch("Plant_sp")
                     + nodecov("N_flowers")
                     + edgecov("spatial_distance_within")
                     + edgecov("spatial_distance_between")
                     + edgecov("fl_overlap_within")
                     + edgecov("fl_overlap_between"))

```

## Unipartite network: compute ERGMs

```{r uni.model.tests.D, echo=TRUE, message= FALSE, warning= TRUE}

set.seed(42)
uni.ergm.fitD <- ergm(uni.ergmD, response ="weight", reference= ~Poisson)   
uni.ergm.fitD.b <- ergm(uni.ergmD.b)   

summary(uni.ergm.fitD) 
summary(uni.ergm.fitD.b) 

mcmc.diagnostics(uni.ergm.fitD)

## predict weighted model

sim.D <- simulate(uni.ergm.fitD, nsim=100, response = "weight", output="edgelist")

sim.D.mat <- list()
for (i in seq_along(sim.D)){
  temp <- get.adjacency(graph.data.frame(sim.D[[i]]), sparse = FALSE, attr='weight')
  sim.D.mat[[i]] <- temp
}
sim.D.mat.mean <- apply(simplify2array(sim.D.mat), 1:2, mean)

sim.D.mat.mean %<>% as.data.frame() %>% rename_at(vars(names(.)), ~attr$Plant_id) %>%
  magrittr::set_rownames(attr$Plant_id) 

sim.D.mat.mean <- get.data.frame(graph.adjacency(as.matrix(sim.D.mat.mean),weighted=TRUE)) %>% 
  rename(Plant_id_1=from, Plant_id_2=to, prob=weight) 
#%>% mutate(prob=range01(prob))

sim.D.mat.mean %<>% left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_1"= "Plant_id")) %>%
  rename(Plant_sp_1 = Plant_sp) %>% 
  left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_2"= "Plant_id")) %>%
  rename(Plant_sp_2 = Plant_sp) %>% mutate(het_con = ifelse(Plant_sp_1==Plant_sp_2, "con", "het")) %>%
  filter(Plant_id_1 != Plant_id_2)

sim.D.summ <- sim.D.mat.mean %>% group_by(Plant_id_1, het_con) %>%
  summarise(mean = mean(prob, na.rm=T)) %>% left_join(freq.int, by=c("Plant_id_1"="Plant_id"))

## predict binary model

predict.D <- predict(uni.ergm.fitD.b, conditional = TRUE, output = "matrix")

predict.D %<>% as.data.frame() %>% rename_at(vars(names(.)), ~attr$Plant_id) %>%
  magrittr::set_rownames(attr$Plant_id) %>% mutate(Plant_id_1=attr$Plant_id) %>% 
  pivot_longer(!Plant_id_1, names_to = "Plant_id_2", values_to = "prob")

predict.D %<>% left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_1"= "Plant_id")) %>%
  rename(Plant_sp_1 = Plant_sp) %>% 
  left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_2"= "Plant_id")) %>%
  rename(Plant_sp_2 = Plant_sp) %>% mutate(het_con = ifelse(Plant_sp_1==Plant_sp_2, "con", "het")) %>%
  filter(Plant_id_1 != Plant_id_2)

predict.D.summ <- predict.D %>% group_by(Plant_id_1, het_con) %>%
  summarise(mean = mean(prob, na.rm=T)) %>% left_join(freq.int, by=c("Plant_id_1"="Plant_id")) 

```

# PLOT E
## Unipartite network: generate the unipartite projection of the plant-pollinator interaction matrix

```{r uni.graph.E, echo=TRUE, message= FALSE, warning= TRUE}

uni <- round((uni.mat.plot[[5]]) *1000, 0)
uni %<>% select(order(colnames(uni))) %>% as.matrix()

attr <- uni.mat.plot[[5]] %>% rownames_to_column("Plant_id") %>% left_join(filter(plant.info, Plot=="E")) %>%
  left_join(select(plant.traits, Plant_id, N_flowers))
attr %<>% group_by(Plant_sp) %>%
  mutate(N_flowers = range01(N_flowers))

# only conspecific individuals

#attr <- filter(attr, Plant_sp=="HPIC")
#uni %<>% 
#    filter(rownames(uni) %in% attr$Plant_id) %>% 
#    select(any_of(attr$Plant_id)) %>% as.matrix()

# remove column and row names
colnames(uni)<-NULL
rownames(uni)<-NULL

```

## Unipartite network: set node attributes in igraph object

```{r uni.nodes.E, echo=TRUE, message= FALSE, warning= TRUE}

uni.g <- graph.adjacency(uni, mode = "undirected", weighted = TRUE, diag = FALSE) # igraph object

V(uni.g)$Plant_id <- attr$Plant_id
V(uni.g)$Plant_sp <- attr$Plant_sp
V(uni.g)$N_flowers <- attr$N_flowers

```

## Unipartite network: set matrices and graphs for model testing (create network object) 

```{r uni.net.E, echo=TRUE, message= FALSE, warning= TRUE}


uni.AA <- get.adjacency(uni.g, attr = "weight") # First separate the igraph object into adjacency matrix and plant attributes

uni.v.attrs <- get.data.frame(uni.g, what="vertices")


uni.net <- network::as.network(as.matrix(uni.AA),
                             directed=FALSE, ignore.eval=FALSE, names.eval='weight')   # network object for ergm 


as.matrix(uni.net,attrname="weight") # We can view the weight attribute as a matrix
#get.edge.attribute(uni.s, "weight")


network::set.vertex.attribute(uni.net, "Plant_id",
                                uni.v.attrs$Plant_id)
network::set.vertex.attribute(uni.net, "Plant_sp",
                                uni.v.attrs$Plant_sp)
network::set.vertex.attribute(uni.net, "N_flowers",
                                uni.v.attrs$N_flowers)

# To include the effects of the spatial and flowering overlap between plant individuals on pollinator sharing

dist <- dist.mat.plot[[5]] 
dist %<>% select(order(colnames(dist)))
dist <- dist[order(rownames(dist)),]

pheno <- pheno.mat.plot[[5]]
pheno %<>% select(order(colnames(pheno)))
pheno <- pheno[order(rownames(pheno)),]

vegan::mantel(as.matrix(pheno), as.matrix(dist))

network::set.network.attribute(uni.net, "distance", as.matrix(dist)) # spatial distance between plants as network attribute
network::get.network.attribute(uni.net, "distance")

network::set.network.attribute(uni.net, "pheno", as.matrix(pheno)) # flowering overlap between plants as network attribute
network::get.network.attribute(uni.net, "pheno")

# evaluation of predictor matrices within and between plant species

sp <- uni.net %v% "Plant_sp"
uni.net %n% "spatial_distance_within" <- range01(uni.net %n% "distance" * outer(sp, sp, `==`))
uni.net %n% "spatial_distance_between" <- range01(uni.net %n% "distance" * outer(sp, sp, `!=`))

uni.net %n% "fl_overlap_within" <- range01(uni.net %n% "pheno" * outer(sp, sp, `==`))
uni.net %n% "fl_overlap_between" <- range01(uni.net %n% "pheno" * outer(sp, sp, `!=`))


```

## Unipartite network: predictor variables for valued ERGMs

```{r uni.models.E, echo=TRUE, message= FALSE, warning= TRUE}


uni.ergm0 <- formula(uni.net ~ sum) 


# test main effects of plant traits in sharing pollinators
uni.ergmE <- formula(uni.net ~ sum 
                     + nodematch("Plant_sp", form= "sum")
                     + nodecov("N_flowers", form= "sum")
                     + edgecov("spatial_distance_within", form="sum")
                     + edgecov("spatial_distance_between", form="sum")
                     + edgecov("fl_overlap_within", form="sum")
                     + edgecov("fl_overlap_between", form="sum"))

uni.ergmE.b <- formula(uni.net ~ edges
                     + nodematch("Plant_sp")
                     + nodecov("N_flowers")
                     + edgecov("spatial_distance_within")
                     + edgecov("spatial_distance_between")
                     + edgecov("fl_overlap_within")
                     + edgecov("fl_overlap_between"))

```

## Unipartite network: compute ERGMs

```{r uni.model.tests.E, echo=TRUE, message= FALSE, warning= TRUE}

set.seed(42)
uni.ergm.fitE <- ergm(uni.ergmE, response ="weight", reference= ~Poisson)   
uni.ergm.fitE.b <- ergm(uni.ergmE.b)   

summary(uni.ergm.fitE) 
summary(uni.ergm.fitE.b) 

mcmc.diagnostics(uni.ergm.fitE)

## predict weighted model

sim.E <- simulate(uni.ergm.fitE, nsim=100, response = "weight", output="edgelist")

sim.E.mat <- list()
for (i in seq_along(sim.E)){
  temp <- get.adjacency(graph.data.frame(sim.E[[i]]), sparse = FALSE, attr='weight')
  sim.E.mat[[i]] <- temp
}
sim.E.mat.mean <- apply(simplify2array(sim.E.mat), 1:2, mean)

sim.E.mat.mean %<>% as.data.frame() %>% rename_at(vars(names(.)), ~attr$Plant_id) %>%
  magrittr::set_rownames(attr$Plant_id) 

sim.E.mat.mean <- get.data.frame(graph.adjacency(as.matrix(sim.E.mat.mean),weighted=TRUE)) %>% 
  rename(Plant_id_1=from, Plant_id_2=to, prob=weight) 
#%>% mutate(prob=range01(prob))

sim.E.mat.mean %<>% left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_1"= "Plant_id")) %>%
  rename(Plant_sp_1 = Plant_sp) %>% 
  left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_2"= "Plant_id")) %>%
  rename(Plant_sp_2 = Plant_sp) %>% mutate(het_con = ifelse(Plant_sp_1==Plant_sp_2, "con", "het")) %>%
  filter(Plant_id_1 != Plant_id_2)

sim.E.summ <- sim.E.mat.mean %>% group_by(Plant_id_1, het_con) %>%
  summarise(mean = mean(prob, na.rm=T)) %>% left_join(freq.int, by=c("Plant_id_1"="Plant_id"))

## predict binary model

predict.E <- predict(uni.ergm.fitE.b, conditional = TRUE, output = "matrix")

predict.E %<>% as.data.frame() %>% rename_at(vars(names(.)), ~attr$Plant_id) %>%
  magrittr::set_rownames(attr$Plant_id) %>% mutate(Plant_id_1=attr$Plant_id) %>% 
  pivot_longer(!Plant_id_1, names_to = "Plant_id_2", values_to = "prob")

predict.E %<>% left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_1"= "Plant_id")) %>%
  rename(Plant_sp_1 = Plant_sp) %>% 
  left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_2"= "Plant_id")) %>%
  rename(Plant_sp_2 = Plant_sp) %>% mutate(het_con = ifelse(Plant_sp_1==Plant_sp_2, "con", "het")) %>%
  filter(Plant_id_1 != Plant_id_2)

predict.E.summ <- predict.E %>% group_by(Plant_id_1, het_con) %>%
  summarise(mean = mean(prob, na.rm=T)) %>% left_join(freq.int, by=c("Plant_id_1"="Plant_id"))

```

# PLOT F
## Unipartite network: generate the unipartite projection of the plant-pollinator interaction matrix

```{r uni.graph.F, echo=TRUE, message= FALSE, warning= TRUE}

uni <- round((uni.mat.plot[[6]]) *1000, 0)
uni %<>% select(order(colnames(uni))) %>% as.matrix()

attr <- uni.mat.plot[[6]] %>% rownames_to_column("Plant_id") %>% left_join(filter(plant.info, Plot=="F")) %>%
  left_join(select(plant.traits, Plant_id, N_flowers))
attr %<>% group_by(Plant_sp) %>%
  mutate(N_flowers = ifelse(Plant_sp!="HPIC", range01(N_flowers), 1))

# only conspecific individuals

#attr <- filter(attr, Plant_sp=="HPIC")
#uni %<>% 
#    filter(rownames(uni) %in% attr$Plant_id) %>% 
#    select(any_of(attr$Plant_id)) %>% as.matrix()

# remove column and row names
colnames(uni)<-NULL
rownames(uni)<-NULL

```

## Unipartite network: set node attributes in igraph object

```{r uni.nodes.F, echo=TRUE, message= FALSE, warning= TRUE}

uni.g <- graph.adjacency(uni, mode = "undirected", weighted = TRUE, diag = FALSE) # igraph object

V(uni.g)$Plant_id <- attr$Plant_id
V(uni.g)$Plant_sp <- attr$Plant_sp
V(uni.g)$N_flowers <- attr$N_flowers

```

## Unipartite network: set matrices and graphs for model testing (create network object) 

```{r uni.net.F, echo=TRUE, message= FALSE, warning= TRUE}


uni.AA <- get.adjacency(uni.g, attr = "weight") # First separate the igraph object into adjacency matrix and plant attributes

uni.v.attrs <- get.data.frame(uni.g, what="vertices")


uni.net <- network::as.network(as.matrix(uni.AA),
                             directed=FALSE, ignore.eval=FALSE, names.eval='weight')   # network object for ergm 


as.matrix(uni.net,attrname="weight") # We can view the weight attribute as a matrix
#get.edge.attribute(uni.s, "weight")


network::set.vertex.attribute(uni.net, "Plant_id",
                                uni.v.attrs$Plant_id)
network::set.vertex.attribute(uni.net, "Plant_sp",
                                uni.v.attrs$Plant_sp)
network::set.vertex.attribute(uni.net, "N_flowers",
                                uni.v.attrs$N_flowers)

# To include the effects of the spatial and flowering overlap between plant individuals on pollinator sharing

dist <- dist.mat.plot[[6]] 
dist %<>% select(order(colnames(dist)))
dist <- dist[order(rownames(dist)),]

pheno <- pheno.mat.plot[[6]]
pheno %<>% select(order(colnames(pheno)))
pheno <- pheno[order(rownames(pheno)),]

vegan::mantel(as.matrix(pheno), as.matrix(dist))

network::set.network.attribute(uni.net, "distance", as.matrix(dist)) # spatial distance between plants as network attribute
network::get.network.attribute(uni.net, "distance")

network::set.network.attribute(uni.net, "pheno", as.matrix(pheno)) # flowering overlap between plants as network attribute
network::get.network.attribute(uni.net, "pheno")

# evaluation of predictor matrices within and between plant species

sp <- uni.net %v% "Plant_sp"
uni.net %n% "spatial_distance_within" <- range01(uni.net %n% "distance" * outer(sp, sp, `==`))
uni.net %n% "spatial_distance_between" <- range01(uni.net %n% "distance" * outer(sp, sp, `!=`))

uni.net %n% "fl_overlap_within" <- range01(uni.net %n% "pheno" * outer(sp, sp, `==`))
uni.net %n% "fl_overlap_between" <- range01(uni.net %n% "pheno" * outer(sp, sp, `!=`))


```

## Unipartite network: predictor variables for valued ERGMs

```{r uni.models.F, echo=TRUE, message= FALSE, warning= TRUE}


uni.ergm0 <- formula(uni.net ~ sum) 


# test main effects of plant traits in sharing pollinators
uni.ergmF <- formula(uni.net ~ sum 
                     + nodematch("Plant_sp", form= "sum")
                     + nodecov("N_flowers", form= "sum")
                     + edgecov("spatial_distance_within", form="sum")
                     + edgecov("spatial_distance_between", form="sum")
                     + edgecov("fl_overlap_within", form="sum")
                     + edgecov("fl_overlap_between", form="sum"))

uni.ergmF.b <- formula(uni.net ~ edges
                     + nodematch("Plant_sp")
                     + nodecov("N_flowers")
                     + edgecov("spatial_distance_within")
                     + edgecov("spatial_distance_between")
                     + edgecov("fl_overlap_within")
                     + edgecov("fl_overlap_between"))


```

## Unipartite network: compute ERGMs

```{r uni.model.tests.F, echo=TRUE, message= FALSE, warning= TRUE}

set.seed(42)
uni.ergm.fitF <- ergm(uni.ergmF, response ="weight", reference= ~Poisson)   
uni.ergm.fitF.b <- ergm(uni.ergmF.b)   

summary(uni.ergm.fitF) 
summary(uni.ergm.fitF.b) 
mcmc.diagnostics(uni.ergm.fitF)

## predict weighted model

sim.F <- simulate(uni.ergm.fitF, nsim=100, response = "weight", output="edgelist")

sim.F.mat <- list()
for (i in seq_along(sim.F)){
  temp <- get.adjacency(graph.data.frame(sim.F[[i]]), sparse = FALSE, attr='weight')
  sim.F.mat[[i]] <- temp
}
sim.F.mat.mean <- apply(simplify2array(sim.F.mat), 1:2, mean)

sim.F.mat.mean %<>% as.data.frame() %>% rename_at(vars(names(.)), ~attr$Plant_id) %>%
  magrittr::set_rownames(attr$Plant_id) 

sim.F.mat.mean <- get.data.frame(graph.adjacency(as.matrix(sim.F.mat.mean),weighted=TRUE)) %>% 
  rename(Plant_id_1=from, Plant_id_2=to, prob=weight) 
#%>% mutate(prob=range01(prob))

sim.F.mat.mean %<>% left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_1"= "Plant_id")) %>%
  rename(Plant_sp_1 = Plant_sp) %>% 
  left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_2"= "Plant_id")) %>%
  rename(Plant_sp_2 = Plant_sp) %>% mutate(het_con = ifelse(Plant_sp_1==Plant_sp_2, "con", "het")) %>%
  filter(Plant_id_1 != Plant_id_2)

sim.F.summ <- sim.F.mat.mean %>% group_by(Plant_id_1, het_con) %>%
  summarise(mean = mean(prob, na.rm=T)) %>% left_join(freq.int, by=c("Plant_id_1"="Plant_id"))

## predict binary model

predict.F <- predict(uni.ergm.fitF.b, conditional = TRUE, output = "matrix")

predict.F %<>% as.data.frame() %>% rename_at(vars(names(.)), ~attr$Plant_id) %>%
  magrittr::set_rownames(attr$Plant_id) %>% mutate(Plant_id_1=attr$Plant_id) %>% 
  pivot_longer(!Plant_id_1, names_to = "Plant_id_2", values_to = "prob")

predict.F %<>% left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_1"= "Plant_id")) %>%
  rename(Plant_sp_1 = Plant_sp) %>% 
  left_join(select(plant.traits, Plant_id, Plant_sp), by=c("Plant_id_2"= "Plant_id")) %>%
  rename(Plant_sp_2 = Plant_sp) %>% mutate(het_con = ifelse(Plant_sp_1==Plant_sp_2, "con", "het")) %>%
  filter(Plant_id_1 != Plant_id_2)

predict.F.summ <- predict.F %>% group_by(Plant_id_1, het_con) %>%
  summarise(mean = mean(prob, na.rm=T)) %>% left_join(freq.int, by=c("Plant_id_1"="Plant_id"))

```

# Effects plots

```{r effect.plots}

### Plot A
effA <- as.data.frame(coef(summary(uni.ergm.fitA))[1:7,c(1:2)])
effA$plot <- "A"
effA$method <- "weighted"
effA$exp <- exp(effA$Estimate)
effA <- tibble::rownames_to_column(effA)
names(effA)[1] <- "variable"
names(effA)[3] <- "se"
effA$low.CI <- exp(confint(uni.ergm.fitA))[,1]
effA$up.CI <-  exp(confint(uni.ergm.fitA))[,2]

effA.b <- as.data.frame(coef(summary(uni.ergm.fitA.b))[1:7,c(1:2)])
effA.b$plot <- "A"
effA.b$method <- "binary"
effA.b$exp <- exp(effA.b$Estimate)
effA.b <- tibble::rownames_to_column(effA.b)
names(effA.b)[1] <- "variable"
names(effA.b)[3] <- "se"
effA.b$low.CI <- exp(confint(uni.ergm.fitA.b))[,1]
effA.b$up.CI <-  exp(confint(uni.ergm.fitA.b))[,2]

### Plot B

effB <- as.data.frame(coef(summary(uni.ergm.fitB))[1:7,c(1:2)])
effB$plot <- "B"
effB$method <- "weighted"
effB$exp <- exp(effB$Estimate)
effB <- tibble::rownames_to_column(effB)
names(effB)[1] <- "variable"
names(effB)[3] <- "se"
effB$low.CI <- exp(confint(uni.ergm.fitB))[,1]
effB$up.CI <-  exp(confint(uni.ergm.fitB))[,2]

effB.b <- as.data.frame(coef(summary(uni.ergm.fitB.b))[1:7,c(1:2)])
effB.b$plot <- "B"
effB.b$method <- "binary"
effB.b$exp <- exp(effB.b$Estimate)
effB.b <- tibble::rownames_to_column(effB.b)
names(effB.b)[1] <- "variable"
names(effB.b)[3] <- "se"
effB.b$low.CI <- exp(confint(uni.ergm.fitB.b))[,1]
effB.b$up.CI <-  exp(confint(uni.ergm.fitB.b))[,2]

### Plot C

effC <- as.data.frame(coef(summary(uni.ergm.fitC))[1:7,c(1:2)])
effC$plot <- "C"
effC$method <- "weighted"
effC$exp <- exp(effC$Estimate)
effC <- tibble::rownames_to_column(effC)
names(effC)[1] <- "variable"
names(effC)[3] <- "se"
effC$low.CI <- exp(confint(uni.ergm.fitC))[,1]
effC$up.CI <-  exp(confint(uni.ergm.fitC))[,2]

effC.b <- as.data.frame(coef(summary(uni.ergm.fitC.b))[1:7,c(1:2)])
effC.b$plot <- "C"
effC.b$method <- "binary"
effC.b$exp <- exp(effC.b$Estimate)
effC.b <- tibble::rownames_to_column(effC.b)
names(effC.b)[1] <- "variable"
names(effC.b)[3] <- "se"
effC.b$low.CI <- exp(confint(uni.ergm.fitC.b))[,1]
effC.b$up.CI <-  exp(confint(uni.ergm.fitC.b))[,2]

### Plot D

effD <- as.data.frame(coef(summary(uni.ergm.fitD))[1:7,c(1:2)])
effD$plot <- "D"
effD$method <- "weighted"
effD$exp <- exp(effD$Estimate)
effD <- tibble::rownames_to_column(effD)
names(effD)[1] <- "variable"
names(effD)[3] <- "se"
effD$low.CI <- exp(confint(uni.ergm.fitD))[,1]
effD$up.CI <-  exp(confint(uni.ergm.fitD))[,2]

effD.b <- as.data.frame(coef(summary(uni.ergm.fitD.b))[1:7,c(1:2)])
effD.b$plot <- "D"
effD.b$method <- "binary"
effD.b$exp <- exp(effD.b$Estimate)
effD.b <- tibble::rownames_to_column(effD.b)
names(effD.b)[1] <- "variable"
names(effD.b)[3] <- "se"
effD.b$low.CI <- exp(confint(uni.ergm.fitD.b))[,1]
effD.b$up.CI <-  exp(confint(uni.ergm.fitD.b))[,2]

### Plot E

effE <- as.data.frame(coef(summary(uni.ergm.fitE))[1:7,c(1:2)])
effE$plot <- "E"
effE$method <- "weighted"
effE$exp <- exp(effE$Estimate)
effE <- tibble::rownames_to_column(effE)
names(effE)[1] <- "variable"
names(effE)[3] <- "se"
effE$low.CI <- exp(confint(uni.ergm.fitE))[,1]
effE$up.CI <-  exp(confint(uni.ergm.fitE))[,2]

effE.b <- as.data.frame(coef(summary(uni.ergm.fitE.b))[1:7,c(1:2)])
effE.b$plot <- "E"
effE.b$method <- "binary"
effE.b$exp <- exp(effE.b$Estimate)
effE.b <- tibble::rownames_to_column(effE.b)
names(effE.b)[1] <- "variable"
names(effE.b)[3] <- "se"
effE.b$low.CI <- exp(confint(uni.ergm.fitE.b))[,1]
effE.b$up.CI <-  exp(confint(uni.ergm.fitE.b))[,2]

### Plot F

effF <- as.data.frame(coef(summary(uni.ergm.fitF))[1:7,c(1:2)])
effF$plot <- "F"
effF$method <- "weighted"
effF$exp <- exp(effF$Estimate)
effF <- tibble::rownames_to_column(effF)
names(effF)[1] <- "variable"
names(effF)[3] <- "se"
effF$low.CI <- exp(confint(uni.ergm.fitF))[,1]
effF$up.CI <-  exp(confint(uni.ergm.fitF))[,2]

effF.b <- as.data.frame(coef(summary(uni.ergm.fitF.b))[1:7,c(1:2)])
effF.b$plot <- "F"
effF.b$method <- "binary"
effF.b$exp <- exp(effF.b$Estimate)
effF.b <- tibble::rownames_to_column(effF.b)
names(effF.b)[1] <- "variable"
names(effF.b)[3] <- "se"
effF.b$low.CI <- exp(confint(uni.ergm.fitF.b))[,1]
effF.b$up.CI <-  exp(confint(uni.ergm.fitF.b))[,2]

### All plots

eff.all <- rbind(effA, effA.b, effB, effB.b, 
                 effC, effC.b, effD, effD.b, 
                 effE, effE.b, effF, effF.b)

df <- data.frame(variable  = c("sum", "nodematch.sum.Plant_sp", "nodecov.sum.N_flowers", 
                                "edgecov.sum.spatial_distance_within", "edgecov.sum.spatial_distance_between",
                                "edgecov.sum.fl_overlap_within", "edgecov.sum.fl_overlap_between",
                                "edges", "nodematch.Plant_sp", "nodecov.N_flowers", 
                                "edgecov.spatial_distance_within", "edgecov.spatial_distance_between",
                                "edgecov.fl_overlap_within", "edgecov.fl_overlap_between"),
                  predictor = c("Baseline", "Plant_sp", "N_flowers", 
                                "spatial_distance_within", "spatial_distance_between",
                                "fl_overlap_within", "fl_overlap_between",
                                "Baseline", "Plant_sp", "N_flowers", 
                                "spatial_distance_within", "spatial_distance_between",
                                "fl_overlap_within", "fl_overlap_between"))

eff.all %<>% left_join(df, by="variable") %>% 
  mutate(predictor = factor(predictor, levels=c("Baseline", "Plant_sp", "N_flowers", 
                                "spatial_distance_within", "spatial_distance_between",
                                "fl_overlap_within", "fl_overlap_between")))

# Figure 2
plot.labs <- c("Plot A", "Plot B", "Plot C", "Plot D", "Plot E", "Plot F")
names(plot.labs) <- c("A", "B", "C", "D", "E", "F")

ggplot(eff.all, aes(x=predictor, y=Estimate, fill=method, group=method)) +
  geom_hline(yintercept=0, linetype="dashed", lwd=0.2, colour="grey50") + 
      geom_bar(alpha=0.6, stat="identity", width=0.6, position=position_dodge(width = 0.8),
               colour="grey50") +
  geom_linerange(aes(ymin = Estimate-se, ymax = Estimate+se),  position = position_dodge2(width = 0.8), size=0.5, colour="grey50") +
  facet_wrap(~plot, nrow=1, scales="free_x", labeller = labeller(plot = plot.labs)) + 
  theme_classic() + coord_flip() + 
  scale_x_discrete(breaks=c("Baseline", "Plant_sp","N_flowers", "spatial_distance_within", "spatial_distance_between", "fl_overlap_within", "fl_overlap_between"), labels=c("Intercept", "Plant species","Number of flowers", "Conspecific \nspatial distance", "Heterospecific \nspatial distance", "Conspecific \nflowering synchrony", "Heterospecific \nflowering synchrony")) + 
  theme(axis.title.y = element_blank(), panel.spacing.y = unit(8, "lines"), 
        panel.spacing.x = unit(2, "lines"),
        strip.background = element_rect(color="white", fill="white", size=1.5), 
        strip.text = element_text(face = "bold", size=12), 
        axis.text.x = element_text(size = 12, margin = margin(t = 10, r = 0, b = 0, l = 0)), 
        axis.text.y = element_text(size = 12, margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        legend.text = element_text(size = 12), legend.title = element_text(size = 12),
        legend.key.size = unit(0.5, "cm"), legend.spacing.y = unit(0.5, 'cm'), legend.position="bottom",
        axis.title=element_text(size=12,face="bold")) + guides(fill = guide_legend(reverse = TRUE), 
                                             colour= guide_legend(reverse = TRUE)) + 
  scale_fill_manual(values = c("white", "grey50"), name = "", 
                      labels = c("Odds of sharing interactions \nbetween plant individuals", "Number of shared interactions \nbetween plant individuals")) +
  guides(fill = guide_legend(byrow = TRUE))


# Table S1

table.output.b <-cbind(coef(summary(uni.ergm.fitA.b)),
      coef(summary(uni.ergm.fitB.b)),
      coef(summary(uni.ergm.fitC.b)),
      coef(summary(uni.ergm.fitD.b)),
      coef(summary(uni.ergm.fitE.b)),
      coef(summary(uni.ergm.fitF.b))
)

# Table S2

table.output.w <-cbind(coef(summary(uni.ergm.fitA)),
      coef(summary(uni.ergm.fitB)),
      coef(summary(uni.ergm.fitC)),
      coef(summary(uni.ergm.fitD)),
      coef(summary(uni.ergm.fitE)),
      coef(summary(uni.ergm.fitF))
)


```

# Heterospecific vs conspecific pollinator sharing probabilities (correlation)

```{r het.con.cor}

n.pol <- int.mat %>% mutate(n_pol=rowSums(.!=0))
predict.all.sum <- rbind(predict.A.summ, predict.B.summ, predict.C.summ, 
                     predict.D.summ, predict.E.summ, predict.F.summ) %>% 
  left_join(select(plant.traits, Plant_id, Plant_sp, Plot), by=c("Plant_id_1"= "Plant_id")) %>% 
  left_join(select(n.pol, Plant_id, n_pol), by=c("Plant_id_1"= "Plant_id")) %>% 
  mutate(n_pol=as.integer(n_pol))

sim.all.sum <- rbind(sim.A.summ, sim.B.summ, sim.C.summ, 
                     sim.D.summ, sim.E.summ, sim.F.summ) %>% 
  left_join(select(plant.traits, Plant_id, Plant_sp, Plot), by=c("Plant_id_1"= "Plant_id")) %>% 
  left_join(select(n.pol, Plant_id, n_pol), by=c("Plant_id_1"= "Plant_id")) %>% 
  mutate(n_pol=as.integer(n_pol))

glimpse(predict.all.sum)

sp.labs <- c("Armeria \n velutina", "Cistus \n libanotis", "Halimium \n calycinum", 
               "Halimium \n halimifolium", "Helichrysum \n picardii", "Lavandula \n pedunculata",
               "Salvia \n rosmarinus", "Stauracanthus \n genistoides","Thymus \n mastichina")
names(sp.labs) <- c("AVEL", "CLIB", "HCOM",
                      "HHAL", "HPIC", "LPED",
                      "ROFF", "SGEN", "TMAS")

sh.labs <- c("Heterospecific", "Conspecific")
names(sh.labs) <- c("het", "con")
scaleFUN <- function(x) sprintf("%.0f", x)


predict.all.long <- predict.all.sum %>%
  pivot_wider(names_from = het_con, values_from = mean) %>% mutate(method="binary")
glimpse(predict.all.long)
predict.all.long$het[is.nan(predict.all.long$het)]<-0
predict.all.long$het[is.na(predict.all.long$het)]<-0

sim.all.long <- sim.all.sum %>%
  pivot_wider(names_from = het_con, values_from = mean) %>% mutate(method="weighted")
glimpse(sim.all.long)
sim.all.long$het[is.nan(sim.all.long$het)]<-0
sim.all.long$het[is.na(sim.all.long$het)]<-0


all.long <- rbind(predict.all.long, sim.all.long)

# binary
b.plot <- ggplot(filter(predict.all.long, Plant_sp!="HPIC"), aes(x=(con), y=(het), color=Plant_sp)) + 
  geom_point(alpha=0.7, aes(size=n_int/2)) + 
  #geom_smooth(method = "lm", se=F, linetype = "dashed")+ 
  facet_wrap(~ Plant_sp, nrow=2, scales="free",  
  labeller = labeller(Plant_sp = sp.labs)) + scale_fill_manual(values=alpha(cols2, 0.8)) +
  scale_color_manual(values=alpha(cols2, 0.8),
                     name = "Plant species", labels = c("Armeria velutina", "Cistus libanotis", 
                                       "Halimium calycinum", "Halimium halimifolium", 
                                       "Lavandula pedunculata", "Salvia rosmarinus", 
                                       "Stauracanthus genistoides", "Thymus mastichina")) +
  theme_base() + theme(text = element_text(size=14), 
    strip.background = element_rect(color="white", fill="white", size=1.5), 
    #strip.text = element_text(face = "italic", size=12),
    strip.text = element_blank(),
    #legend.position = "none",
    legend.text=element_text(face="italic"),
    plot.background = element_blank(),
    axis.title.x = element_text(size=14, margin = margin(t = 10, r = 0, b = 0, l = 0)),
    axis.title.y = element_text(size=14, margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  xlab("Odds of sharing at least one interaction with conspecific plant individuals") + 
  ylab("Odds of sharing at least one interaction \nwith heterospecific plant individuals") + 
  scale_x_log10() + scale_y_log10() +
  theme(panel.spacing.x = unit(5, "mm")) + guides(size = "none", fill="none")

# range of variation
glimpse(predict.all.long) 
mean(predict.all.long$con, na.rm=T)
sd(predict.all.long$con, na.rm=T)
mean(predict.all.long$het, na.rm=T)
sd(predict.all.long$het, na.rm=T)
predict.all.long %>% group_by(Plant_sp) %>% 
  summarise(min_con=min(con, na.rm=T),
            max_con=max(con, na.rm=T),
            min_het=min(het, na.rm=T),
            max_het=max(het, na.rm=T)) %>% ungroup() %>%
  summarise(mean_min_con=mean(min_con),
            sd_min_con=sd(min_con),
            mean_max_con=mean(max_con),
            sd_max_con=sd(max_con),
            mean_min_het=mean(min_het),
            sd_min_het=sd(min_het),
            mean_max_het=mean(max_het),
            sd_max_het=sd(max_het))


# weighted
w.plot <- ggplot(filter(sim.all.long, Plant_sp!= "HPIC"), aes(x=(con), y=(het), color=Plant_sp)) + 
  geom_point(alpha=0.7, aes(size=n_int/2)) + 
  #geom_smooth(method = "lm", se=F, linetype = "dashed") + 
  facet_wrap(~ Plant_sp, nrow=2, scales="free",  
  labeller = labeller(Plant_sp = sp.labs)) + scale_fill_manual(values=alpha(cols2, 0.8)) +
  scale_color_manual(values=alpha(cols2, 0.8), 
                     name = "Plant species", labels = c("Armeria velutina", "Cistus libanotis", 
                                       "Halimium calycinum", "Halimium halimifolium", 
                                       "Lavandula pedunculata", "Salvia rosmarinus", 
                                       "Stauracanthus genistoides", "Thymus mastichina")) + 
  theme_base() + theme(text = element_text(size=14),
    panel.background = element_rect(fill = alpha("grey30", alpha=0.1)), plot.background = element_blank(),
    strip.background = element_rect(color="white", fill="white", size=1.5), 
    #strip.text = element_text(face = "italic", size=12),
    strip.text = element_blank(),
    #legend.position = "none",
    legend.text=element_text(face="italic"),
    axis.title.x = element_text(size=14, margin = margin(t = 10, r = 0, b = 0, l = 0)),
    axis.title.y = element_text(size=14, margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  xlab("Number of shared interactions with conspecific plant individuals") + ylab("Number of shared interactions with \nheterospecific plant individuals") + 
  scale_x_log10() + scale_y_log10() +
  theme(panel.spacing.x = unit(5, "mm")) + guides(size = "none")

# range of variation
glimpse(sim.all.long) 
mean(sim.all.long$con, na.rm=T)
sd(sim.all.long$con, na.rm=T)
mean(sim.all.long$het, na.rm=T)
sd(sim.all.long$het, na.rm=T)
sim.all.long %>% group_by(Plant_sp) %>% 
  summarise(min_con=min(con, na.rm=T),
            max_con=max(con, na.rm=T),
            min_het=min(het, na.rm=T),
            max_het=max(het, na.rm=T)) %>% ungroup() %>%
  summarise(mean_min_con=mean(min_con),
            sd_min_con=sd(min_con),
            mean_max_con=mean(max_con),
            sd_max_con=sd(max_con),
            mean_min_het=mean(min_het),
            sd_min_het=sd(min_het),
            mean_max_het=mean(max_het),
            sd_max_het=sd(max_het))

# Figure 3
b.plot / w.plot + plot_layout(guides = "collect")


## test correlation between conspecific and heterospecific sharing (binary and weighted)

hist(log(test2$het))
test2 <- filter(predict.all.long, het>0, con>0)
lm.con.het.b <- lmer(log(het) ~ log(con) + (1|Plant_sp) + (1|Plot),
                   test2)
summary(lm.con.het.b)

min(test2$con)
max(test2$con)
min(test2$het)
max(test2$het)

hist(log((sim.all.long)$het))
test1 <- filter(sim.all.long, het>0, con>0)
lm.con.het.w <- lmer(log(het) ~ log(con) + (1|Plant_sp) + (1|Plot),
                   test1)
summary(lm.con.het.w)

min(test1$con)
max(test1$con)
min(test1$het)
max(test1$het)

```

# Heterospecific vs conspecific sharing probabilities (boxplots)

```{r het.con.boxplot}

# binary
predict.A %<>% mutate(Plot="A", method="binary")
predict.B %<>% mutate(Plot="B", method="binary")
predict.C %<>% mutate(Plot="C", method="binary")
predict.D %<>% mutate(Plot="D", method="binary")
predict.E %<>% mutate(Plot="E", method="binary")
predict.F %<>% mutate(Plot="F", method="binary")

# weighted
sim.A.mat.mean %<>% mutate(Plot="A", method="weighted")
sim.B.mat.mean %<>% mutate(Plot="B", method="weighted")
sim.C.mat.mean %<>% mutate(Plot="C", method="weighted")
sim.D.mat.mean %<>% mutate(Plot="D", method="weighted")
sim.E.mat.mean %<>% mutate(Plot="E", method="weighted")
sim.F.mat.mean %<>% mutate(Plot="F", method="weighted")

predict.all <- rbind(predict.A, predict.B, predict.C, 
                     predict.D, predict.E, predict.F,
                     sim.A.mat.mean, sim.B.mat.mean, sim.C.mat.mean, 
                     sim.D.mat.mean, sim.E.mat.mean, sim.F.mat.mean)

labs <- c("Odds of sharing at least one interaction \n with other plant individuals",
          "Number of shared interactions \n with other plant individuals")
names(labs) <- c("binary", "weighted")

## this is necessary to colour the panel background differently for het and con
tp <- unique(predict.all[,c('method','Plant_sp_1')])
tp$prob <- 1
tp$het_con <- "het"

# Figure S3
het.con.plot <- ggplot(filter(predict.all, prob<1000), aes(x=het_con, y=(prob), group=het_con, fill=Plant_sp_1, colour=Plant_sp_1)) +
  geom_boxplot(aes(fill=Plant_sp_1), alpha = 0.5, 
               outlier.shape=NA, width=0.1, position= position_nudge(x=-.2)) + 
  geom_jitter(position=position_jitter(width=0.1, height=0), size=0.1, alpha=0.3) +
  facet_grid(method~Plant_sp_1, labeller = labeller(Plant_sp_1 = sp.labs, method=labs), scales="free") +
  scale_color_manual(values=(cols2)) +
  scale_fill_manual(values=alpha(cols2, 0.8)) + theme_base() + theme(plot.background = element_blank(),
   strip.background = element_rect(color="white", fill="white", size=1.5), 
   strip.text.x = element_text(face = "italic", size=14),
   strip.text.y = element_text(size=14),
   axis.title.x = element_text(size=14, margin = margin(t = 10, r = 0, b = 0, l = 0)),
   axis.title.y = element_text(size=14, margin = margin(t = 0, r = 10, b = 0, l = 0)),
   legend.position = "none") +
  xlab("") + ylab("") + 
        geom_rect(data = subset(tp,method == 'weighted'),aes(fill = method),xmin = -Inf,xmax = Inf,
            ymin = -Inf,ymax = Inf,alpha = 0.15) + 
  scale_x_discrete(labels=c("het" = "Het", "con" = "Con"))



```

# Network plots

```{r net.plots}

# Example for plot A
uni <- round((uni.mat.plot[[1]]) *1000, 0)

# set species as node attributes
plant.id.sp <- read.csv("Data/individual_plants_id.csv", sep=";")
plant.id.sp <- plant.id.sp[,c(3,5)]
plant.int <- left_join(mutate(uni, Plant_id=rownames(uni)), plant.id.sp, by ="Plant_id")

# merge species with color
colors <- data.frame(Plant_sp=names(cols2), color=cols2, row.names=NULL)
col.species <- merge(x=plant.int, 
                     y=colors, 
                     by= "Plant_sp") 
str(col.species)
col.species[is.na(col.species)] <- 0 # replace NA with 0 
col.species %<>% filter_if(is.numeric, any_vars(. != 0)) %>% 
  select_if(~ any(. != 0))

# create igraph object
bipartite.web <- graph.adjacency(as.matrix(col.species[2:(length(col.species)-2)]), mode = "undirected", weighted = T, diag = FALSE) 


V(bipartite.web)$name <- c(col.species$Plant_id)
V(bipartite.web)$plant_sp <- c(col.species$Plant_sp)
V(bipartite.web)$size <- 6
#E(bipartite.web)$width <- log(E(bipartite.web)$weight)
E(bipartite.web)$width <- 1
V(bipartite.web)$color <- c(col.species$color)


par(oma=c(0,0,0,0)) # all sides have 3 lines of space
par(mar=c(0,0,0,0) + 0.1)

plot(bipartite.web, vertex.label=NA, vertex.frame.color="white", 
     edge.color=adjustcolor("grey70", alpha.f = .7), 
     vertex.color = adjustcolor(V(bipartite.web)$color, alpha.f = .7),
     layout= layout_with_fr(bipartite.web), 
     vertex.size=V(bipartite.web)$size, rescale=T, asp = 1, edge.curved = 0.3)
#legend("bottomleft", bty = "n",
#       legend=colors$Plant_sp,
#       col=colors$color, border=NA, cex=0.7, pch=16, pt.cex=1.5)



```

